\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-09 ccs/ex.tex
nits

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). Theoretically, the size of a boolean multiplication circuit is quadratic in the bit-width, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g., comparisons, bit-shifts, etc.

>>>>

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). The size of a boolean multiplication circuit is quadratic in the bit-width, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g., comparisons, bit-shifts, etc.
Further implementation details can be found in~\sectionref{impl}.

### 2018-05-09 ccs/impl.tex
nits

\vspace{-0.1in}
\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides support for Arithmetic computation based on \cite{autoS}, and boolean computations based on GMW~\cite{gmw} as well as Yao's garbled circuits~\cite{yao}. Although \tool can generate code for both kinds of boolean computations, we have observed better performance when using the garbled circuits
and use it in our evaluation. Hence, \tool generated code uses Arithmetic computation and garbled circuits based boolean computations.
We use $128$ bits of security and OT
extension-based arithmetic multiplication triplets generation. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

@@

The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations, e.g., by
%For instance, if boolean shares of a variable are available in scope and the %variable is involved in
%an addition then \tool performs the addition in boolean rather than first %coercing boolean to arithmetic
%and then performing an arithmetic addition. 
%However, multiplication is always performed in arithmetic as the cost of a %boolean multiplication is much higher than the cost of coercing from boolean %to arithmetic, performing an arithmetic multiplication, and then coercing from %arithmetic to boolean~\cite{aby}.
%Other optimizations include
the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.
These optimizations are standard compiler
optimizations~\cite{dragonbook}, and we rely on their correctness to
maintain the correctness and security of the optimized programs.

>>>>

\vspace{-0.1in}
\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides support for Arithmetic computations based on \cite{autoS}, and boolean computations based on GMW~\cite{gmw} as well as Yao's garbled circuits~\cite{yao}. Although \tool can generate code for both kinds of boolean computations, we have observed better performance when using  garbled circuits
and use it in our evaluation. Hence, \tool generated code uses Arithmetic computations and garbled circuits based boolean computations.
We use $128$ bits of security and OT
extension-based arithmetic multiplication triplets generation. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

@@

The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations, e.g., by
%For instance, if boolean shares of a variable are available in scope and the %variable is involved in
%an addition then \tool performs the addition in boolean rather than first %coercing boolean to arithmetic
%and then performing an arithmetic addition. 
%However, multiplication is always performed in arithmetic as the cost of a %boolean multiplication is much higher than the cost of coercing from boolean %to arithmetic, performing an arithmetic multiplication, and then coercing from %arithmetic to boolean~\cite{aby}.
%Other optimizations include
the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.
These optimizations are standard compiler
optimizations~\cite{dragonbook}, and we rely on their correctness
(optimizations preserve outputs and well-typedness) to
maintain the security of the optimized programs.
